\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-09-14 paper.tex
Revise wording

\section{\normalsize\textbf{Related Work}}
The economic value of huge amount of data emerges, several researchers have started to explore the design of data marketplace. The Third Party Auditors (TPAs)-based frameworks\cite{TPA} is far from being satisfactory due to the unstandardize data format dynamic nature of IoT data. Therefore a decentralized data integrity validation and trading process has been proposed recent years, and distributed ledger technology (DLT) is considered a solution, which has the immutable data storage feature that the existence of data can be trusted and no longer rely on any third party authority.

Data Integrity as a Service (DIaaS) is a blockchain based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) allows both data provider and consumer to validate data integrity by comparing hashes on Ethereum smart contract\cite{smartContract} and Cloud Server. Moreover, Ethereum smart contract can also realize the purchase agreement, including authoriziation and the penalization. However, the architecture of DIaaS needs highly trust on CSS, if CSS is malicious or crashed, that will cause losses to both providers and consumers. Also, the performance analysis shows that IoT devices have low efficiency interacting with Ethereum due to the time-consuming Proof-of-Work(PoW) process.

By solving the inefficiency of the Blockchain, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency for the IoT industry based on a revolutionary distributed ledger technology, the \textbf{Tangle}, which enables zero-transaction. On top of that, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, a second layer data communication protocol which allows to emit, access and verify an encrypted data stream over the Tangle where privacy and integrity meet.

On the basis of the Tangle and MAM, IOTA foundation launched a Data Marketplace\cite{IOTADataMarket} which is suitable for IoT streaming data that not only allows data providers to put data on Tangle without any trusted cloud services, but also allow providers and consumers to trade on Tangle and protect privacy and assure data integrity from source with MAM. Nevertheless, the platform design is centralized, new devices require manual approval from IOTA foundation to be visible in the marketplace. Also, interacting with Tangle is still the bottleneck for low-level devices especially in an unstable network or electricity environment.

A different framework design proposed by Gupta, S.Kanhere and Jurdak\cite{3tierDataMarket} could reduce the burden of low-level devices as mentioned. The infrastructure is a 3-tier decentralized data marketplace architectural design with Ethereum smart contract which consists of provider, consumer and broker. Where broker is a trustless and highly resourced device that will facilitate the trading of data between the consumer and providers. However, the data integrity and authentication of each participant are still future work.

The sustainability of IoT economic system is under discussion by Dusit Niyato et al.\cite{UtilityStruct}. They evaluated the utility structure of data trading and presented game theory model.  Data marketplace organizers can determine their policies to ensure a sustainable system with the Nash Equilibrium found by game theory and the utility structure. However, refund and subscription economy were not mentioned in their work.

The previous work proposed different solution to specific issues of data marketplace. In this paper, we had an  overall design of decentralized data marketplace that takes care of data integrity and trading procedure such as buyout and subscibing to future data on distributed ledger.

>>>>

\section{\normalsize\textbf{Related Work}}
As the economic value of huge amount of data emerges, several researchers have started to explore the design of data marketplace. The Third Party Auditors (TPAs)-based frameworks\cite{TPA} is far from being satisfactory due to the unstandardized data format dynamic nature of IoT data. Therefore a decentralized data integrity validation and trading process has been proposed recent years, and distributed ledger technology (DLT) is considered a solution, which has the immutable data storage feature that the existence of data can be trusted and no longer rely on any third party authority.

Data Integrity as a Service (DIaaS) is a blockchain based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) which allows both data provider and consumer to validate data integrity by comparing hashes on Ethereum smart contracts\cite{smartContract} and cloud servers. Moreover, Ethereum smart contract can also realize the purchase agreement, including authorization and penalization. However, the architecture of DIaaS needs high trust on the CSS. If the CSS is malicious or has crashed, losses to both providers and consumers will result. Also, performance analysis shows that IoT devices have low efficiency interacting with Ethereum due to the time-consuming Proof-of-Work(PoW) process.

To address the inefficiency of the Blockchain, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency for the IoT industry based on a revolutionary distributed ledger technology, the \textbf{Tangle}, which enables zero-transaction. On top of that, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, is provided for a second layer data communication protocol which allows transmission, access, and verification of an encrypted data stream over the Tangle where privacy and integrity meet.

Based on Tangle and MAM, the IOTA foundation launched a data marketplace\cite{IOTADataMarket} which is suitable for IoT streaming data that not only allows data providers to put data on Tangle without any trusted cloud services, but also allow providers and consumers to trade on Tangle with privacy protected and assurance of data integrity from source with MAM. Nevertheless, the platform design is centralized, new devices require manual approval from the IOTA foundation to be visible in the marketplace. Also, interacting with Tangle is still the bottleneck for low-level devices especially in an unstable network or electrically noisy environment.

A different framework design proposed by Gupta, S.Kanhere and Jurdak\cite{3tierDataMarket} could reduce the burden of low-level devices as mentioned. The infrastructure is a 3-tier decentralized data marketplace architectural design with Ethereum smart contracts which consist of providers, consumers and brokers. The broker is a trustless and highly resourced device that will facilitate the trading of data between the consumer and providers. However, the data integrity and authentication of each participant is still forthcoming.

The sustainability of IoT economic system was under discussion by Dusit Niyato et al.\cite{UtilityStruct}. They evaluated the utility structure of data trading and presented game theory model.  Data marketplace organizers can determine their policies to ensure a sustainable system with the Nash Equilibrium found by game theory and the utility structure. However, refund and subscription economy were not mentioned in their work.

Such work proposed different solutions to specific issues of data marketplaces. In this paper, we had an overall design of decentralized data marketplace that handles data integrity and trading procedures such as buyout and subscriptions to future data on a distributed ledger.
